---
title: "NFL Scouting Report"
format:
  html:
    toc: true
    theme: cosmo
    embed-resources: true
execute:
  echo: false
  warning: false
  message: false
params:
  offense_team: "KC"
  defense_team: "SF"
  season: 2025
  situation: "all"
  project_dir: ""
---

```{r setup}
library(tidyverse)
library(scales)
library(gt)
library(htmltools)

project_dir <- params$project_dir

if (is.null(project_dir) || identical(project_dir, "")) {
  project_dir <- getwd()
}

project_dir <- normalizePath(project_dir, winslash = "/", mustWork = FALSE)

if (!file.exists(file.path(project_dir, "R", "helpers.R"))) {
  parent_dir <- dirname(project_dir)
  if (file.exists(file.path(parent_dir, "R", "helpers.R"))) {
    project_dir <- parent_dir
  }
}

source(file.path(project_dir, "R", "helpers.R"))
source(file.path(project_dir, "R", "metrics.R"))
source(file.path(project_dir, "R", "branding.R"))

scouting_data <- readRDS(file.path(project_dir, "data", "processed", "scouting_data.rds"))

offense_data <- get_team_unit_situation_data(
  data = scouting_data,
  team = params$offense_team,
  season = params$season,
  unit = "offense",
  situation = params$situation
)

defense_data <- get_team_unit_situation_data(
  data = scouting_data,
  team = params$defense_team,
  season = params$season,
  unit = "defense",
  situation = params$situation
)

offense_overview <- calculate_team_overview(offense_data, "offense")
defense_overview <- calculate_team_overview(defense_data, "defense")
offense_proe <- calculate_proe_summary(offense_data, "offense")
defense_proe <- calculate_proe_summary(defense_data, "defense")
matchup_overview <- calculate_matchup_overview(offense_data, defense_data)
matchup_down <- calculate_matchup_down_table(offense_data, defense_data)
matchup_field_zone <- calculate_matchup_field_zone_table(offense_data, defense_data)

offense_color <- get_primary_color(params$offense_team)
defense_color <- get_primary_color(params$defense_team)

summary_text <- build_matchup_summary_text(
  offense_team = params$offense_team,
  defense_team = params$defense_team,
  matchup_overview = matchup_overview
)

metric_card <- function(title, value, subtitle, color) {
  div(
    class = "metric-card",
    style = paste0("border-top: 5px solid ", color, ";"),
    h4(title),
    h2(value),
    p(subtitle)
  )
}
```

<style>
body {
  background-color: #f6f8fb;
}

.quarto-title-block {
  padding: 24px 28px;
  border-radius: 18px;
  background: linear-gradient(135deg, #111827, #374151);
  color: white;
  margin-bottom: 24px;
}

h1, h2, h3 {
  font-weight: 750;
}

.report-hero {
  padding: 24px;
  border-radius: 20px;
  background: white;
  box-shadow: 0 4px 18px rgba(0,0,0,0.08);
  margin-bottom: 24px;
}

.matchup-title {
  font-size: 34px;
  font-weight: 800;
  margin-bottom: 8px;
}

.matchup-subtitle {
  font-size: 16px;
  color: #6b7280;
}

.summary-box {
  padding: 20px 24px;
  border-radius: 18px;
  background: #ffffff;
  border-left: 6px solid #111827;
  box-shadow: 0 4px 18px rgba(0,0,0,0.06);
  font-size: 17px;
  line-height: 1.6;
  margin-bottom: 24px;
}

.metric-grid {
  display: grid;
  grid-template-columns: repeat(4, minmax(160px, 1fr));
  gap: 16px;
  margin: 22px 0;
}

.metric-card {
  background: white;
  border-radius: 18px;
  padding: 18px 20px;
  box-shadow: 0 4px 18px rgba(0,0,0,0.06);
}

.metric-card h4 {
  margin: 0;
  font-size: 14px;
  color: #6b7280;
  text-transform: uppercase;
  letter-spacing: 0.04em;
}

.metric-card h2 {
  margin: 8px 0 4px;
  font-size: 30px;
}

.metric-card p {
  margin: 0;
  color: #6b7280;
  font-size: 13px;
}

.section-card {
  padding: 22px;
  border-radius: 18px;
  background: white;
  box-shadow: 0 4px 18px rgba(0,0,0,0.06);
  margin-bottom: 24px;
}

.gt_table {
  font-size: 15px;
}
</style>

<div class="report-hero">
  <div class="matchup-title">`r params$offense_team` Offense vs `r params$defense_team` Defense</div>
  <div class="matchup-subtitle">
    Season: `r params$season` &nbsp; | &nbsp; Situation: `r params$situation`
  </div>
</div>

# Executive Summary

<div class="summary-box">
`r summary_text`
</div>

# Key Metrics

<div class="metric-grid">
```{r, results='asis'}
tagList(
  metric_card(
    "Offense EPA/Play",
    format_num(offense_overview$epa_per_play),
    paste(params$offense_team, "offensive efficiency"),
    offense_color
  ),
  metric_card(
    "Defense EPA/Play",
    format_num(defense_overview$epa_per_play),
    paste(params$defense_team, "defensive efficiency"),
    defense_color
  ),
  metric_card(
    "Offense PROE",
    format_pct(offense_proe$proe),
    "Pass rate over expected",
    offense_color
  ),
  metric_card(
    "Opponent PROE Allowed",
    format_pct(defense_proe$proe),
    "Passing tendency faced",
    defense_color
  )
)
```
</div>

# Offense Profile

<div class="section-card">

```{r}
offense_overview %>%
  transmute(
    Plays = plays,
    `Pass Rate` = percent(pass_rate, accuracy = 0.1),
    `EPA/Play` = round(epa_per_play, 3),
    `Success Rate` = percent(success_rate, accuracy = 0.1),
    `Explosive Rate` = percent(explosive_rate, accuracy = 0.1)
  ) %>%
  gt() %>%
  tab_header(
    title = paste(params$offense_team, "Offensive Overview")
  ) %>%
  tab_options(
    table.font.names = "Inter",
    heading.title.font.size = 20
  )
```

</div>

# Defense Profile

<div class="section-card">

```{r}
defense_overview %>%
  transmute(
    Plays = plays,
    `Pass Rate Faced` = percent(pass_rate, accuracy = 0.1),
    `Defensive EPA/Play` = round(epa_per_play, 3),
    `Stop Rate` = percent(success_rate, accuracy = 0.1),
    `Explosive Prevention Rate` = percent(explosive_rate, accuracy = 0.1)
  ) %>%
  gt() %>%
  tab_header(
    title = paste(params$defense_team, "Defensive Overview")
  ) %>%
  tab_options(
    table.font.names = "Inter",
    heading.title.font.size = 20
  )
```

</div>

# Matchup Overview

<div class="section-card">

```{r}
matchup_overview %>%
  mutate(
    offense_value = case_when(
      metric %in% c("Pass Rate", "Success Rate", "Explosive Rate", "PROE") ~ percent(offense_value, accuracy = 0.1),
      TRUE ~ as.character(round(offense_value, 3))
    ),
    defense_value = case_when(
      metric %in% c("Pass Rate", "Success Rate", "Explosive Rate", "PROE") ~ percent(defense_value, accuracy = 0.1),
      TRUE ~ as.character(round(defense_value, 3))
    ),
    matchup_edge = case_when(
      metric %in% c("Pass Rate", "Success Rate", "Explosive Rate", "PROE") ~ percent(matchup_edge, accuracy = 0.1),
      TRUE ~ as.character(round(matchup_edge, 3))
    )
  ) %>%
  rename(
    Metric = metric,
    `Offense Value` = offense_value,
    `Defense Value` = defense_value,
    `Matchup Edge` = matchup_edge
  ) %>%
  gt() %>%
  tab_header(
    title = "Offense vs Defense Matchup Snapshot"
  ) %>%
  tab_options(
    table.font.names = "Inter",
    heading.title.font.size = 20
  )
```

</div>

# Down-by-Down Matchup

<div class="section-card">

```{r}
matchup_down %>%
  mutate(
    offense_pass_rate = percent(offense_pass_rate, accuracy = 0.1),
    defense_pass_rate = percent(defense_pass_rate, accuracy = 0.1),
    pass_rate_gap = percent(pass_rate_gap, accuracy = 0.1),
    offense_epa = round(offense_epa, 3),
    defense_epa = round(defense_epa, 3),
    epa_gap = round(epa_gap, 3)
  ) %>%
  rename(
    Down = down,
    `Off Pass Rate` = offense_pass_rate,
    `Off EPA` = offense_epa,
    `Def Pass Rate Faced` = defense_pass_rate,
    `Def EPA` = defense_epa,
    `Pass Rate Gap` = pass_rate_gap,
    `EPA Gap` = epa_gap
  ) %>%
  gt() %>%
  tab_header(
    title = "Down-by-Down Tendencies"
  ) %>%
  tab_options(
    table.font.names = "Inter",
    heading.title.font.size = 20
  )
```

</div>

# Field Zone Matchup

<div class="section-card">

```{r}
matchup_field_zone %>%
  mutate(
    offense_pass_rate = percent(offense_pass_rate, accuracy = 0.1),
    defense_pass_rate = percent(defense_pass_rate, accuracy = 0.1),
    pass_rate_gap = percent(pass_rate_gap, accuracy = 0.1),
    offense_epa = round(offense_epa, 3),
    defense_epa = round(defense_epa, 3),
    epa_gap = round(epa_gap, 3)
  ) %>%
  rename(
    `Field Zone` = field_zone,
    `Off Pass Rate` = offense_pass_rate,
    `Off EPA` = offense_epa,
    `Def Pass Rate Faced` = defense_pass_rate,
    `Def EPA` = defense_epa,
    `Pass Rate Gap` = pass_rate_gap,
    `EPA Gap` = epa_gap
  ) %>%
  gt() %>%
  tab_header(
    title = "Field Position Tendencies"
  ) %>%
  tab_options(
    table.font.names = "Inter",
    heading.title.font.size = 20
  )
```

</div>

# Notes

This report is generated from the Shiny scouting app using play-by-play data and the selected situation filter.